```{r echo=FALSE}
data <- read.csv("tidy_data.csv")
```

## Generation from the UCI HAR Dataset
### Required Libraries
* plyr
* data.table

### Rerunning the code
1. source the **run_analysis.R** file
2. execute the imported **run_analysis()** function
  _optional_: The function will return a data.table to memory.

### run_analysis.R process explained
1. loads required libraries (data.table & plyr)
2. **inside of run_analysis** defines the convenience paste method %p% which is used extensively throughout the code.
3. Defines destination files, Destination Directories, and Source File (for downloading)
4. Downloads the file if the uncompressed directory has not been detected _if it's been detected, skip to step 6_
5. Unzips and deletes the original zip file
6. Read in the **features.txt** file provided from the dataset. These define the meaning of each measurement.
    * Will assign an index and measurement column name for quick reference later
7. Reads in the **activity_labels.txt** file for consumption later
    * Will assign an index and activity column names to the read data for quick reference
8. Defines read function
    1. Defines the working directory **wd**
    2. Reads the associated data files for each set _replace "type" below with the test or train respectively_
        * **subject_type.txt** to determine the subjects for each reading
        * **y_type.txt** to determine the activity done at the time
        * **x_type.txt** to receive all of the measurements observed.
    3. Extracts only the **standard deviation** and **mean** measurements recorded from the _x_type.txt_ dataset above.
    4. Defines the appropriate column names for the measurements extracted above from the **features.txt** file read earlier.
    5. Binds all of the data read into a single data.frame
9. Calls the read function twice. Once for **test** and once for **train**
10. Merges the two data sets together
11. Rewrites the activity column with **mutate** from dplyr to be clearly readable
12. Writes the data set to **tidy_data.csv**
13. Returns the data.table representation of the data.

## tidy_data.csv column names
```{r}
colnames(data)
```